Breast cancer is the second leading cause of 
cancer deaths among women and screening 
mammography has been found to reduce 
mortality. It is necessary to build 
mammography image recognition systems. 
Previous solutions for mammography image 
recognition are usually based on hand-crafted 
features methods and use but limited in 
specific situations. Also, some methods 
utilize simple deep learning network, which 
can not extract the full feature of mammography,
for example, GoogleNet, VGG16, ResNet, DenseNet, etc.
In this paper, we propose a deep learning based 
approach with multiple feature fusion transfer 
learning strategy. Firstly, we obtain the 
training data from an open data set called 
DDSM images. Then we employ data augment 
methods, and training a deep convolutional 
neural network to extract image features and 
conduct the object detection job. 
A pre-trained model is used to initialize the 
network and help extract the basic features.
Furthermore, we propose a fusion method that 
makes use of multiple transfer learning models 
in inference, to improve the accuracy on the 
test set. Importantly, we take a strategy 
applied by hash learning in the deep network 
is cited to enhance the generalization ability 
of the model and solve the challenge of 
high-dimensional calculation in deep learning. 
In the end, regression analysis to analyze 
the object position. The experimental results 
prove that our method achieves high accuracy on 
the mammography image object detection 
and inspection task.